Hydra Battles and Cie

### 2021-01-21 doc/chapter-primrec.tex
add an exercises/ directory

\begin{remark}
Note that the Ackermann function is a counter-example to the (false) statement:
\begin{quote}
  ``Let $f$ be a function of type \texttt{naryFunc\,2}. If, for any $n$, the fonction $f(n)$ is primitive recursive , then f is primitive recursive.''
\end{quote}
\end{remark}
\end{project}

>>>>

\begin{remark}
Note that the Ackermann function is a counter-example to the (false) statement:
\begin{quote}
{\color{red}
  ``Let $f$ be a function of type \texttt{naryFunc\,2}. If, for any $n$, the fonction $f(n)$ is primitive recursive, then f is primitive recursive.''}
\end{quote}
\end{remark}
\end{project}
